---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# R.inat.fxns

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/R.inat.fxns)](https://CRAN.R-project.org/package=R.inat.fxns)
<!-- badges: end -->

The goal of R.inat.fxns is to provide some functions that make downloading iNat observations from multiple projects easy. Please use responsibly.

## Installation

You can install the development version of R.inat.fxns from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("samherniman/R.inat.fxns")
```

## Example

Load the package with:

```{r example}
library(R.inat.fxns)
```

Make a list of iNat project slugs to download from

```{r projects}
projects_vec <- c(
  "city-nature-challenge-2022-greater-vancouver", 
  "city-nature-challenge-2022-delta-bc",
  "city-nature-challenge-2022-richmond-bc",
  "city-nature-challenge-2022-surrey-bc",
  "city-nature-challenge-2022-tri-cities-british-columbia"
)
```

Download all the observations in each project

```{r eval = FALSE}
obs_sf <- download_many_projects(projects_vec)
```


